### 2016-11-04 thesis/intro/intro.tex
tmp commit

\subsubsection{Role of hormones on arcuate nucleus neurons}
\label{ssub:role_of_hormones_on_arcuate_nucleus_neurons}

>>>>

\subsubsection{Leptin-melanocortin pathway}
\label{ssub:leptin_melanocortin_pathway}

Leptin-melanocortin pathway is the pathway in which the level of satiety is controlled and regulated.
In this pathway, both the orexogenic and anorexogenic neurons have crucial roles in controlling the satiety of the individual, and therefore their eating behaviour.

When a satiety-controlling hormone, such as leptin, reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.

Firstly, when an orexogenic \gls{npy}/\gls{agrp} neurons are stimulated,

\subsubsection{Role of hormones in leptin-melanocortin pathway}
\label{ssub:role_of_hormones_in_leptin_melanocortin_pathway}

There are many hormones in your body that regulates various physiological aspects of your body.
Out of the many, four hormones have an important role in regulating the satiety of an individual: ghrelin, leptin, insulin, and \gls{pyy}.

Ghrelin is a hormone produced mainly in the stomach that has a role in meal initiation and food intake \citep{Kohno2003}.

Leptin, on the otherhand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.

Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.

The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.
\citep{Batterham2002}
